Evaluating infectious disease forecasts with allocation scoring rules

### 2023-05-26 alloscore_manuscript/allocation.tex
Uptaded intro paragraph 1

\usepackage{soul}
\usepackage{color}
\def\elr#1{{\color{cyan}\textbf{ELR:[#1]}}}
\def\apg#1{{\color{red}\textbf{APG:[#1]}}}

@@

%Grohskopf "Prevention and Control of Seasonal Influenza with Vaccines: Recommendations of the Advisory Committee on Immunization Practices — United States, 2022–23 Influenza Season" - Current CDC recommendations state that "Timing, intensity, and severity of the 2022-23 influenze season cannot be predicted"

@@

Infectious disease forecasting models have emerged as important tools in public health decision making. Predictions of disease dynamics have been used to inform decision-making about a wide variety of measures designed to reduce disease spread and/or mitigate the severity of disease outcomes. In a simple example, estimates of expected onset of flu season have been used to inform national vaccination strategies  \cite{igboh2023timing}, and forecasts of ebola dynamics have been used to allocate surveillance resources \cite{meltzer2014estimating}. Other examples of past decision making applications of infectious disease forecasts include the allocation of limited medical supplies such as ventilators \cite{bertsimas2021predictionsCOVID}, implementation of social distancing measures such as stay-at-home policies, planning site selection for vaccine trials \cite{bertsimas2021predictionsCOVID}, and strategies for public health communication campaigns.

For example, estimates of expected onset of flu have been used to inform national flu vaccination strategies \cite{igboh2023timing}, and allocation of ebola surveillance resources \cite{meltzer2014estimating}.  Other past decision making applications of infectious disease forecasts include the allocation of limited medical supplies such as ventilators \cite{bertsimas2021predictionsCOVID}, implementation of social distancing measures such as stay-at-home policies, planning site selection for vaccine trials \cite{bertsimas2021predictionsCOVID}, and strategies for public health communication campaigns.

>>>>

\usepackage{soul}
\usepackage{color}
\def\elr#1{{\color{cyan}\textbf{ELR:[#1]}}}
\def\apg#1{{\color{red}\textbf{APG:[#1]}}}
\def\bwr#1{{\color{violet}\textbf{BWR:[#1]}}}

@@

@@

Infectious disease forecasting models have emerged as important tools in public health decision making. Predictions of disease dynamics have been used to inform decision-making about a wide variety of measures designed to reduce disease spread and/or mitigate the severity of disease outcomes. For example, estimates of expected onset of flu season were used to inform national vaccination strategies  \citep{igboh2023timing}, and forecasts of ebola dynamics were used to allocate surveillance resources \citep{meltzer2014estimating, rainisch2015regional}. In April of 2022, the Centers for Disease Control and Prevention (CDC) announced the launch of the Center for Forecasting and Outbreak Analytics (CFA) to translate disease forecasts into decision-making \citep{cdc2022cfa}. \cite{bertsimas2021predictionsCOVID} developed tools to inform decision making from infectious disease forecasts, which have been used to to inform allocation of limited medical supplies such as ventilators, ICU capacity planning, and vaccine distribution strategy. Models developed by \cite{fox_real-time_2022} have been used to inform resource and care site planning, as well as community guidelines for masking, traveling, dining and shopping \citep{utnews2022}.  \bwr{Figure out these news site citations!}
